---
title: "Do you have your smartphone with you? Behavioral barriers for measuring everyday activities with smartphone sensors"
author: "Florian Keusch, Alexander Wenz, & Frederick G. Conrad"
date: 
output:
  html_document:
    number_sections: false
    toc: true
    toc_float: true
    toc_depth: 3
---

<style type="text/css">
h1.title {
  font-size: 28px;
}
h1 { /* Header 1 */
  font-size: 24px;
}
h2 { /* Header 2 */
  font-size: 20px;
}
h3 { /* Header 3 */
  font-size: 16px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE}
## set working directory
setwd("C:/Users/Alexander/Documents/1 Research/3 Published/19 Behavioral barriers/Data/v2")

## load packages
library(readr)
library(dplyr)
library(qwraps2)
library(margins)
library(knitr)
library(kableExtra)
library(DescTools)
library(stargazer)
library(broom)
library(MASS)

## import data
load("Behavioral barriers_Sample2.RData")
```

# Table 2. Descriptive statistics.
```{r, results='asis'}
options(qwraps2_markup = "markdown")
sample_2 <- data %>%
  dplyr::select(gender, agegroup1, edu, os, frequse, skills, phonedependent)
summary <- sample_2 %>%
  qsummary(.,n_perc_args = list(digits = 1, show_symbol = TRUE)) 
summary_table(sample_2, summary)
```

# Table 3. Prevalence of behavioral barriers to measuring mobility, physical activity, and sleep using smartphone sensors.
```{r, results='asis'}
options(qwraps2_markup = "markdown")
sample_2 <- data %>%
  dplyr::select(sharing, turnedoff, outhomeuse, outhomelocation, athomelocation, nightstatusandlocation)
summary <- sample_2 %>%
  qsummary(.,n_perc_args = list(digits = 1, show_symbol = TRUE)) 
summary_table(sample_2, summary)
```

# Table A3. Descriptive statistics of measures before recoding.
```{r, results='asis'}
options(qwraps2_markup = "markdown")
sample_2 <- data %>%
  dplyr::select(frequse1, skills1, hasdesktop, hastablet, outhomeuse1, outhomelocation1, nightstatus1, nightlocation1, athomelocation1)
summary <- sample_2 %>%
  qsummary(.,n_perc_args = list(digits = 1, show_symbol = TRUE)) 
summary_table(sample_2, summary)
```

```{r}
summary(data$hrsturnedon)
sd(data$hrsturnedon, na.rm=TRUE)
```

# Table A4. Coding rules for implausible responses to questions about sleep duration.
```{r, results='asis'}
sleepcoding <- data.frame("N Weekday"=c(table(data$flag1)[[2]], table(data$flag2)[[2]], table(data$flag3)[[2]], table(data$flag4)[[2]]),
                          "N Weekend"=c(table(data$flag10)[[2]], table(data$flag20)[[2]], table(data$flag30)[[2]], table(data$flag40)[[2]]))

kable(sleepcoding)
```

# Table A5. Descriptive statistics of everyday activities Sample 2.
```{r, results='asis'}
options(qwraps2_markup = "markdown")
sample_2 <- data %>%
  dplyr::select(kmtravelwd_adj1, kmtravelwdlog, kmtravelwe_adj1, kmtravelwelog, vpa, vpa1, vpaordinal, mpa, mpa1, mpaordinal, hrssitwd_adj1, hrssitwe_adj1, sleephrswd_adj1, sleephrswe_adj1)
summary <- sample_2 %>%
  qsummary(.,n_perc_args = list(digits = 1, show_symbol = TRUE)) 
summary_table(sample_2, summary)
```
