---
title: "Do you have your smartphone with you? Behavioral barriers for measuring everyday activities with smartphone sensors"
author: "Florian Keusch, Alexander Wenz, & Frederick G. Conrad"
date: 
output:
  html_document:
    number_sections: false
    toc: true
    toc_float: true
    toc_depth: 3
---

<style type="text/css">
h1.title {
  font-size: 28px;
}
h1 { /* Header 1 */
  font-size: 24px;
}
h2 { /* Header 2 */
  font-size: 20px;
}
h3 { /* Header 3 */
  font-size: 16px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE}
## set working directory
setwd("C:/Users/Alexander/Documents/1 Research/3 Published/19 Behavioral barriers/Data/v2")

## load packages
library(readr)
library(dplyr)
library(qwraps2)
library(margins)
library(knitr)
library(kableExtra)
library(DescTools)
library(stargazer)
library(broom)
library(MASS)

## import data
load("Behavioral barriers_Sample2.RData")
```

# Table A7. Logistic regression models of smartphone usage behaviors on sociodemographic and smartphone-related characteristics Sample 2.
## Smartphone shared with another person
```{r}
order <- c("genderFemale", "agegroup125-30", "agegroup131-40", "agegroup141-50", "agegroup151-60", "agegroup161+", "eduHigh school degree", "eduCollege degree", "osAndroid", "osOther OS", "frequseEvery day", "frequseSeveral times a day", "skillsIntermediate", "skillsAdvanced", "phonedependentYes")

data$sharing <- ifelse(data$sharing=="Smartphone shared with another person", 1,
                       ifelse(data$sharing=="Not shared with another person", 0, NA))
sharing <- glm(sharing~gender+agegroup1+edu+os+frequse+skills+phonedependent, data, family="binomial")

sharing_outsave <- summary(margins(sharing)) %>%
  mutate(sample=2,
         dependent=1,
         independent=factor) %>%
  dplyr::select(sample, dependent, independent, AME, lower, upper) %>%
  slice(match(order, independent))

sharing_outprint <- summary(margins(sharing)) %>%
  dplyr::select(factor, AME, SE, p) %>%
  slice(match(order, factor))

kable(sharing_outprint, digits=3) %>%
  kable_styling()

nobs(sharing)
round(PseudoR2(sharing, which="Nagelkerke"), digits=3)
```

## Smartphone not always on
```{r}
data$turnedoff <- ifelse(data$turnedoff=="Smartphone not always on", 1,
                       ifelse(data$turnedoff=="Always on", 0, NA))
turnedoff <- glm(turnedoff~gender+agegroup1+edu+os+frequse+skills+phonedependent, data, family="binomial")

turnedoff_outsave <- summary(margins(turnedoff)) %>%
  mutate(sample=2,
         dependent=2,
         independent=factor) %>%
  dplyr::select(sample, dependent, independent, AME, lower, upper) %>%
  slice(match(order, independent))

turnedoff_outprint <- summary(margins(turnedoff)) %>%
  dplyr::select(factor, AME, SE, p) %>%
  slice(match(order, factor))

kable(turnedoff_outprint, digits=3) %>%
  kable_styling()

nobs(turnedoff)
round(PseudoR2(turnedoff, which="Nagelkerke"), digits=3)
```

## Smartphone left at home
```{r}
data$outhomeuse <- ifelse(data$outhomeuse=="Smartphone left at home", 1,
                       ifelse(data$outhomeuse=="Not left at home", 0, NA))
outhomeuse <- glm(outhomeuse~gender+agegroup1+edu+os+frequse+skills+phonedependent, data, family="binomial")

outhomeuse_outsave <- summary(margins(outhomeuse)) %>%
  mutate(sample=2,
         dependent=3,
         independent=factor) %>%
  dplyr::select(sample, dependent, independent, AME, lower, upper) %>%
  slice(match(order, independent))

outhomeuse_outprint <- summary(margins(outhomeuse)) %>%
  dplyr::select(factor, AME, SE, p) %>%
  slice(match(order, factor))

kable(outhomeuse_outprint, digits=3) %>%
  kable_styling()

nobs(outhomeuse)
round(PseudoR2(outhomeuse, which="Nagelkerke"), digits=3)
```

## Smartphone carried in purse/backpack/bag
```{r}
data$outhomelocation <- ifelse(data$outhomelocation=="In purse/backpack/bag", 1,
                       ifelse(data$outhomelocation=="Close to body", 0, NA))
outhomelocation <- glm(outhomelocation~gender+agegroup1+edu+os+frequse+skills+phonedependent, data, family="binomial")

outhomelocation_outsave <- summary(margins(outhomelocation)) %>%
  mutate(sample=2,
         dependent=4,
         independent=factor) %>%
  dplyr::select(sample, dependent, independent, AME, lower, upper) %>%
  slice(match(order, independent))

outhomelocation_outprint <- summary(margins(outhomelocation)) %>%
  dplyr::select(factor, AME, SE, p) %>%
  slice(match(order, factor))

kable(outhomelocation_outprint, digits=3) %>%
  kable_styling()

nobs(outhomelocation)
round(PseudoR2(outhomelocation, which="Nagelkerke"), digits=3)
```

## Smartphone left stationary when at home
```{r}
data$athomelocation <- ifelse(data$athomelocation=="Smartphone left stationary when at home", 1,
                       ifelse(data$athomelocation=="Not left stationary when at home", 0, NA))
athomelocation <- glm(athomelocation~gender+agegroup1+edu+os+frequse+skills+phonedependent, data, family="binomial")

athomelocation_outsave <- summary(margins(athomelocation)) %>%
  mutate(sample=2,
         dependent=5,
         independent=factor) %>%
  dplyr::select(sample, dependent, independent, AME, lower, upper) %>%
  slice(match(order, independent))

athomelocation_outprint <- summary(margins(athomelocation)) %>%
  dplyr::select(factor, AME, SE, p) %>%
  slice(match(order, factor))

kable(athomelocation_outprint, digits=3) %>%
  kable_styling()

nobs(athomelocation)
round(PseudoR2(athomelocation, which="Nagelkerke"), digits=3)
```

## Smartphone turned off or in other room at night
```{r}
data$nightstatusandlocation <- ifelse(data$nightstatusandlocation=="Smartphone turned off or in other room at night", 1,
                       ifelse(data$nightstatusandlocation=="Turned on and in same room at night", 0, NA))
nightstatusandlocation <- glm(nightstatusandlocation~gender+agegroup1+edu+os+frequse+skills+phonedependent, data, family="binomial")

nightstatusandlocation_outsave <- summary(margins(nightstatusandlocation)) %>%
  mutate(sample=2,
         dependent=6,
         independent=factor) %>%
  dplyr::select(sample, dependent, independent, AME, lower, upper) %>%
  slice(match(order, independent))

nightstatusandlocation_outprint <- summary(margins(nightstatusandlocation)) %>%
  dplyr::select(factor, AME, SE, p) %>%
  slice(match(order, factor))

kable(nightstatusandlocation_outprint, digits=3) %>%
  kable_styling()

nobs(nightstatusandlocation)
round(PseudoR2(nightstatusandlocation, which="Nagelkerke"), digits=3)

## save regression output in csv file
output_barriers <- bind_rows(sharing_outsave, turnedoff_outsave, outhomeuse_outsave, outhomelocation_outsave, athomelocation_outsave, nightstatusandlocation_outsave)
write_csv(output_barriers, "output_barriers_sample2.csv")
```
