---
title: "Do you have your smartphone with you? Behavioral barriers for measuring everyday activities with smartphone sensors"
author: "Florian Keusch, Alexander Wenz, & Frederick G. Conrad"
date: 
output:
  html_document:
    number_sections: false
    toc: true
    toc_float: true
    toc_depth: 3
---

<style type="text/css">
h1.title {
  font-size: 28px;
}
h1 { /* Header 1 */
  font-size: 24px;
}
h2 { /* Header 2 */
  font-size: 20px;
}
h3 { /* Header 3 */
  font-size: 16px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE}
## set working directory
setwd("C:/Users/Alexander/Documents/1 Research/3 Published/19 Behavioral barriers/Data/v2")

## load packages
library(readr)
library(dplyr)
library(qwraps2)
library(margins)
library(knitr)
library(kableExtra)
library(DescTools)
library(stargazer)
library(broom)
library(MASS)

## import data
load("Behavioral barriers_Sample2.RData")
```

# Table A8. OLS regression models of travel distance on smartphone usage behaviors and sociodemographic and smartphone-related characteristics Sample 2.
```{r, results='asis'}
data <- data %>%
  mutate(turnedoff=relevel(turnedoff, ref="Always on"),
         outhomeuse=relevel(outhomeuse, ref="Not left at home"),
         sharing=relevel(sharing, ref="Not shared with another person"))

wdmobility <- lm(kmtravelwd_adj1~turnedoff+outhomeuse+sharing, data)
wdmobilityc <- lm(kmtravelwd_adj1~turnedoff+outhomeuse+sharing+gender+agegroup1+edu+os+frequse+skills+phonedependent, data)
wemobility <- lm(kmtravelwe_adj1~turnedoff+outhomeuse+sharing, data)
wemobilityc <- lm(kmtravelwe_adj1~turnedoff+outhomeuse+sharing+gender+agegroup1+edu+os+frequse+skills+phonedependent, data)

wdmobility_outsave <- tidy(wdmobility, conf.int=TRUE, conf.level=0.95) %>%
  mutate(sample=2,
         model=1,
         dependent=1,
         independent=term,
         lower=conf.low,
         upper=conf.high) %>%
  dplyr::select(sample, model, dependent, independent, estimate, lower, upper)

wdmobilityc_outsave <- tidy(wdmobilityc, conf.int=TRUE, conf.level=0.95) %>%
  mutate(sample=2,
         model=2,
         dependent=1,
         independent=term,
         lower=conf.low,
         upper=conf.high) %>%
  dplyr::select(sample, model, dependent, independent, estimate, lower, upper) %>%
  filter(independent=="(Intercept)"|independent=="turnedoffSmartphone not always on"|independent=="outhomeuseSmartphone left at home" |independent=="sharingSmartphone shared with another person")

wemobility_outsave <- tidy(wemobility, conf.int=TRUE, conf.level=0.95) %>%
  mutate(sample=2,
         model=1,
         dependent=2,
         independent=term,
         lower=conf.low,
         upper=conf.high) %>%
  dplyr::select(sample, model, dependent, independent, estimate, lower, upper)

wemobilityc_outsave <- tidy(wemobilityc, conf.int=TRUE, conf.level=0.95) %>%
  mutate(sample=2,
         model=2,
         dependent=2,
         independent=term,
         lower=conf.low,
         upper=conf.high) %>%
  dplyr::select(sample, model, dependent, independent, estimate, lower, upper) %>%
  filter(independent=="(Intercept)"|independent=="turnedoffSmartphone not always on"|independent=="outhomeuseSmartphone left at home"|independent=="sharingSmartphone shared with another person")

wdmobilitylog <- lm(kmtravelwdlog~turnedoff+outhomeuse+sharing, data)
wdmobilitylogc <- lm(kmtravelwdlog~turnedoff+outhomeuse+sharing+gender+agegroup1+edu+os+frequse+skills+phonedependent, data)
wemobilitylog <- lm(kmtravelwelog~turnedoff+outhomeuse+sharing, data)
wemobilitylogc <- lm(kmtravelwelog~turnedoff+outhomeuse+sharing+gender+agegroup1+edu+os+frequse+skills+phonedependent, data)

wdmobilitylog_outsave <- tidy(wdmobilitylog, conf.int=TRUE, conf.level=0.95) %>%
  mutate(sample=2,
         model=1,
         dependent=1,
         independent=term,
         lower=conf.low,
         upper=conf.high) %>%
  dplyr::select(sample, model, dependent, independent, estimate, lower, upper)

wdmobilitylogc_outsave <- tidy(wdmobilitylogc, conf.int=TRUE, conf.level=0.95) %>%
  mutate(sample=2,
         model=2,
         dependent=1,
         independent=term,
         lower=conf.low,
         upper=conf.high) %>%
  dplyr::select(sample, model, dependent, independent, estimate, lower, upper) %>%
  filter(independent=="(Intercept)"|independent=="turnedoffSmartphone not always on"|independent=="outhomeuseSmartphone left at home"|independent=="sharingSmartphone shared with another person")

wemobilitylog_outsave <- tidy(wemobilitylog, conf.int=TRUE, conf.level=0.95) %>%
  mutate(sample=2,
         model=1,
         dependent=2,
         independent=term,
         lower=conf.low,
         upper=conf.high) %>%
  dplyr::select(sample, model, dependent, independent, estimate, lower, upper)

wemobilitylogc_outsave <- tidy(wemobilitylogc, conf.int=TRUE, conf.level=0.95) %>%
  mutate(sample=2,
         model=2,
         dependent=2,
         independent=term,
         lower=conf.low,
         upper=conf.high) %>%
  dplyr::select(sample, model, dependent, independent, estimate, lower, upper) %>%
  filter(independent=="(Intercept)"|independent=="turnedoffSmartphone not always on"|independent=="outhomeuseSmartphone left at home"|independent=="sharingSmartphone shared with another person")

stargazer(wdmobility, wdmobilityc, wdmobilitylog, wdmobilitylogc, wemobility, wemobilityc, wemobilitylog, wemobilitylogc, header=FALSE, align=TRUE, type='html', intercept.bottom = FALSE, digits=2, star.cutoffs = c(0.05, 0.01, 0.001), omit.stat=c("ser", "f"), dep.var.caption  = "Travel distance(km)", dep.var.labels   = c("Weekday", "Weekday(log)", "Weekend", "Weekend(log)"), model.names=TRUE, order=c("Constant", "sharing", "turnedoff", "outhomeuse", "gender", "agegroup1", "edu", "os", "frequse", "skills", "phonedependent"))
```

# Table A9. Logistic regression models of physical activity on smartphone usage behaviors and sociodemographic and smartphone-related characteristics Sample 2.
## Vigorous physical activity: Ordinal response
```{r}
data <- data %>%
  mutate(outhomelocation=relevel(outhomelocation, ref="Close to body"),
         athomelocation=relevel(athomelocation, ref="Not left stationary when at home"))

order_pa <- c("sharingSmartphone shared with another person", "turnedoffSmartphone not always on", "outhomeuseSmartphone left at home", "outhomelocationIn purse/backpack/bag", "athomelocationSmartphone left stationary when at home")
order_pac <- c("sharingSmartphone shared with another person", "turnedoffSmartphone not always on", "outhomeuseSmartphone left at home", "outhomelocationIn purse/backpack/bag", "athomelocationSmartphone left stationary when at home", "genderFemale", "agegroup125-30", "agegroup131-40", "agegroup141-50", "agegroup151-60", "agegroup161+", "eduHigh school degree", "eduCollege degree", "osAndroid", "osOther OS", "frequseEvery day", "frequseSeveral times a day", "skillsIntermediate", "skillsAdvanced", "phonedependentYes")

vpaordinal <- polr(vpaordinal~turnedoff+outhomeuse+outhomelocation+athomelocation+sharing, data, Hess=TRUE)
vpacordinal <- polr(vpaordinal~turnedoff+outhomeuse+outhomelocation+athomelocation+sharing+gender+agegroup1+edu+os+frequse+skills+phonedependent, data, Hess=TRUE)

vpaordinal_outsave <- summary(margins(vpaordinal)) %>%
  mutate(sample=2,
         model=1,
         dependent=3,
         independent=factor,
         estimate=AME) %>%
  dplyr::select(sample, model, dependent, independent, estimate, lower, upper)

vpacordinal_outsave <- summary(margins(vpacordinal)) %>%
  mutate(sample=2,
         model=2,
         dependent=3,
         independent=factor,
         estimate=AME) %>%
  dplyr::select(sample, model, dependent, independent, estimate, lower, upper) %>%
  filter(independent=="turnedoffSmartphone not always on"|independent=="outhomeuseSmartphone left at home"|independent=="outhomelocationIn purse/backpack/bag"|independent=="athomelocationSmartphone left stationary when at home"|independent=="sharingSmartphone shared with another person")

vpaordinal_outprint <- summary(margins(vpaordinal)) %>%
  dplyr::select(factor, AME, SE, p) %>%
  slice(match(order_pa, factor))

vpacordinal_outprint <- summary(margins(vpacordinal)) %>%
  dplyr::select(factor, AME, SE, p) %>%
  slice(match(order_pac, factor))

kable(vpaordinal_outprint, digits=3) %>%
  kable_styling()

nobs(vpaordinal)
round(PseudoR2(vpaordinal, which="Nagelkerke"), digits=3)

kable(vpacordinal_outprint, digits=3) %>%
  kable_styling()

nobs(vpacordinal)
round(PseudoR2(vpacordinal, which="Nagelkerke"), digits=3)
```

## Moderate physical activity: Ordinal response
```{r}
mpaordinal <- polr(mpaordinal~turnedoff+outhomeuse+outhomelocation+athomelocation+sharing, data, Hess=TRUE)
mpacordinal <- polr(mpaordinal~turnedoff+outhomeuse+outhomelocation+athomelocation+sharing+gender+agegroup1+edu+os+frequse+skills+phonedependent, data, Hess=TRUE)

mpaordinal_outsave <- summary(margins(mpaordinal)) %>%
  mutate(sample=2,
         model=1,
         dependent=4,
         independent=factor,
         estimate=AME) %>%
  dplyr::select(sample, model, dependent, independent, estimate, lower, upper)

mpacordinal_outsave <- summary(margins(mpacordinal)) %>%
  mutate(sample=2,
         model=2,
         dependent=4,
         independent=factor,
         estimate=AME) %>%
  dplyr::select(sample, model, dependent, independent, estimate, lower, upper) %>%
  filter(independent=="turnedoffSmartphone not always on"|independent=="outhomeuseSmartphone left at home"|independent=="outhomelocationIn purse/backpack/bag"|independent=="athomelocationSmartphone left stationary when at home"|independent=="sharingSmartphone shared with another person")

mpaordinal_outprint <- summary(margins(mpaordinal)) %>%
  dplyr::select(factor, AME, SE, p) %>%
  slice(match(order_pa, factor))

mpacordinal_outprint <- summary(margins(mpacordinal)) %>%
  dplyr::select(factor, AME, SE, p) %>%
  slice(match(order_pac, factor))

kable(mpaordinal_outprint, digits=3) %>%
  kable_styling()

nobs(mpaordinal)
round(PseudoR2(mpaordinal, which="Nagelkerke"), digits=3)

kable(mpacordinal_outprint, digits=3) %>%
  kable_styling()

nobs(mpacordinal)
round(PseudoR2(mpacordinal, which="Nagelkerke"), digits=3)
```

# Table A10. OLS regression models of sedentary behavior on smartphone usage behaviors and sociodemographic and smartphone-related characteristics Sample 2.
```{r, results='asis'}
wdsit <- lm(hrssitwd_adj1~turnedoff+outhomeuse+outhomelocation+athomelocation+sharing, data)
wdsitc <- lm(hrssitwd_adj1~turnedoff+outhomeuse+outhomelocation+athomelocation+sharing+gender+agegroup1+edu+os+frequse+skills+phonedependent, data)
wesit <- lm(hrssitwe_adj1~turnedoff+outhomeuse+outhomelocation+athomelocation+sharing, data)
wesitc <- lm(hrssitwe_adj1~turnedoff+outhomeuse+outhomelocation+athomelocation+sharing+gender+agegroup1+edu+os+frequse+skills+phonedependent, data)

wdsit_outsave <- tidy(wdsit, conf.int=TRUE, conf.level=0.95) %>%
  mutate(sample=2,
         model=1,
         dependent=5,
         independent=term,
         lower=conf.low,
         upper=conf.high) %>%
  dplyr::select(sample, model, dependent, independent, estimate, lower, upper)

wdsitc_outsave <- tidy(wdsitc, conf.int=TRUE, conf.level=0.95) %>%
  mutate(sample=2,
         model=2,
         dependent=5,
         independent=term,
         lower=conf.low,
         upper=conf.high) %>%
  dplyr::select(sample, model, dependent, independent, estimate, lower, upper) %>%
  filter(independent=="(Intercept)"|independent=="turnedoffSmartphone not always on"|independent=="outhomeuseSmartphone left at home"|independent=="outhomelocationIn purse/backpack/bag"|independent=="athomelocationSmartphone left stationary when at home"|independent=="sharingSmartphone shared with another person")

wesit_outsave <- tidy(wesit, conf.int=TRUE, conf.level=0.95) %>%
  mutate(sample=2,
         model=1,
         dependent=6,
         independent=term,
         lower=conf.low,
         upper=conf.high) %>%
  dplyr::select(sample, model, dependent, independent, estimate, lower, upper)

wesitc_outsave <- tidy(wesitc, conf.int=TRUE, conf.level=0.95) %>%
  mutate(sample=2,
         model=2,
         dependent=6,
         independent=term,
         lower=conf.low,
         upper=conf.high) %>%
  dplyr::select(sample, model, dependent, independent, estimate, lower, upper) %>%
  filter(independent=="(Intercept)"|independent=="turnedoffSmartphone not always on"|independent=="outhomeuseSmartphone left at home"|independent=="outhomelocationIn purse/backpack/bag"|independent=="athomelocationSmartphone left stationary when at home"|independent=="sharingSmartphone shared with another person")

stargazer(wdsit, wdsitc, wesit, wesitc, header=FALSE, align=TRUE, type='html', intercept.bottom = FALSE, digits=2, star.cutoffs = c(0.05, 0.01, 0.001), omit.stat=c("ser", "f"), dep.var.caption  = "Sedentary behavior(hrs)", dep.var.labels   = c("Weekday", "Weekend"), model.names=TRUE, order=c("Constant", "sharing", "turnedoff", "outhomeuse", "outhomelocation", "athomelocation", "gender", "agegroup1", "edu", "os", "frequse", "skills", "phonedependent"))
```

# Table A11. OLS regression models of sleep duration on smartphone usage behaviors and sociodemographic and smartphone-related characteristics Sample 2.
```{r, results='asis'}
data <- data %>%
  mutate(nightstatusandlocation=relevel(nightstatusandlocation, ref="Turned on and in same room at night"))

wdsleep <- lm(sleephrswd_adj1~turnedoff+nightstatusandlocation+sharing, data)
wdsleepc <- lm(sleephrswd_adj1~turnedoff+nightstatusandlocation+sharing+gender+agegroup1+edu+os+frequse+skills+phonedependent, data)
wesleep <- lm(sleephrswe_adj1~turnedoff+nightstatusandlocation+sharing, data)
wesleepc <- lm(sleephrswe_adj1~turnedoff+nightstatusandlocation+sharing+gender+agegroup1+edu+os+frequse+skills+phonedependent, data)

wdsleep_outsave <- tidy(wdsleep, conf.int=TRUE, conf.level=0.95) %>%
  mutate(sample=2,
         model=1,
         dependent=7,
         independent=term,
         lower=conf.low,
         upper=conf.high) %>%
  dplyr::select(sample, model, dependent, independent, estimate, lower, upper)

wdsleepc_outsave <- tidy(wdsleepc, conf.int=TRUE, conf.level=0.95) %>%
  mutate(sample=2,
         model=2,
         dependent=7,
         independent=term,
         lower=conf.low,
         upper=conf.high) %>%
  dplyr::select(sample, model, dependent, independent, estimate, lower, upper) %>%
  filter(independent=="(Intercept)"|independent=="turnedoffSmartphone not always on"|independent=="nightstatusandlocationSmartphone turned off or in other room at night"|independent=="sharingSmartphone shared with another person")

wesleep_outsave <- tidy(wesleep, conf.int=TRUE, conf.level=0.95) %>%
  mutate(sample=2,
         model=1,
         dependent=8,
         independent=term,
         lower=conf.low,
         upper=conf.high) %>%
  dplyr::select(sample, model, dependent, independent, estimate, lower, upper)

wesleepc_outsave <- tidy(wesleepc, conf.int=TRUE, conf.level=0.95) %>%
  mutate(sample=2,
         model=2,
         dependent=8,
         independent=term,
         lower=conf.low,
         upper=conf.high) %>%
  dplyr::select(sample, model, dependent, independent, estimate, lower, upper) %>%
  filter(independent=="(Intercept)"|independent=="turnedoffSmartphone not always on"|independent=="nightstatusandlocationSmartphone turned off or in other room at night"|independent=="sharingSmartphone shared with another person")

stargazer(wdsleep, wdsleepc, wesleep, wesleepc, header=FALSE, align=TRUE, type='html', intercept.bottom = FALSE, digits=2, star.cutoffs = c(0.05, 0.01, 0.001), omit.stat=c("ser", "f"), dep.var.caption  = "Sleep duration(hrs)", dep.var.labels   = c("Weekday", "Weekend"), model.names=TRUE, order=c("Constant", "sharing", "turnedoff", "nightstatusandlocation", "gender", "agegroup1", "edu", "os", "frequse", "skills", "phonedependent"))

## save regression output in csv file
output_targets <- bind_rows(wdmobility_outsave, wdmobilityc_outsave, wemobility_outsave, wemobilityc_outsave,
                            vpaordinal_outsave, vpacordinal_outsave, mpaordinal_outsave, mpacordinal_outsave,
                            wdsit_outsave, wdsitc_outsave, wesit_outsave, wesitc_outsave,
                            wdsleep_outsave, wdsleepc_outsave, wesleep_outsave, wesleepc_outsave)
write_csv(output_targets, "output_targets.csv")

output_targets_log <- bind_rows(wdmobilitylog_outsave, wdmobilitylogc_outsave, wemobilitylog_outsave, wemobilitylogc_outsave)
write_csv(output_targets_log, "output_targets_log.csv")
```
